Evaluation of performances

### 2020-01-10 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE, verbose = TRUE)

```{r}
df_perf = getBMRPerformances(bm_aggregated, as.df = T) %>%
  mutate(task.id = recode_factor(task.id,
    `defoliation-all-plots-HR` = "HR",
    `defoliation-all-plots-VI` = "VI",
    `defoliation-all-plots-NRI` = "NRI",
    `defoliation-all-plots-HR-NRI` = "HR-NRI",
    `defoliation-all-plots-HR-VI` = "HR-VI",
    `defoliation-all-plots-HR-NRI-VI` = "HR-NRI-VI",
  )) %>%
  tidyr::separate(learner.id, c("learner_group", "filter"),
    remove = FALSE,
    sep = " "
  ) 
```

@@

```{r performance-results, warning=FALSE, dev = c("png", "pdf")}
results_aggr <- df_perf %>%
  mutate(filter = replace(filter, is.na(filter), "NF")) %>%
  mutate(learner_group = recode_factor(learner_group, `XG` = "XGBOOST")) %>%
  group_by(learner_group, task.id) %>%
  # get the best performance per learner and task
  # this is better than summarise() because we can keep additional columns
  # in constrast to summariuse which only keeps the grouping columns and the
  # summarised one
  slice(which.min(rmse_aggr))

results_aggr %>%
  ggplot(aes(x = rmse_aggr, y = task.id)) +
  # geom_jitter(aes(color = learner_group), size = 2, width = 0, height = 0.3) +
  # geom_dotplot(aes(fill = learner_group), binaxis="y",
  #                        stackdir="up") +
  geom_beeswarm(groupOnX = FALSE, aes(color = learner_group), size = 3) +
  scale_color_nejm(breaks = sort(levels(results_aggr$learner_group))) +
  labs(x = "RMSE", y = "Task", color = "Learner") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 70)) +
  geom_label_repel(
    # subset data to remove out of bounds values
    data = results_aggr[results_aggr$rmse_aggr < 100, ],
    # from ggbeeswarm, avoid overlapping of points by labels
    position = position_quasirandom(),
    aes(label = paste(filter, ",", round(rmse_aggr, 2))),
    size = 2.8,
    min.segment.length = 0.1,
    seed = 123,
    point.padding = 0.5
  ) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    axis.text.y = element_text(angle = 45),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

comb %>%
  ggplot(aes(x = rmse_aggr, y = learner_group)) +
  geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 3) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Filter") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 47)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    axis.text.y = element_text(angle = 45),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

comb_borda %>%
  ggplot(aes(x = rmse_aggr, y = learner_group)) +
  geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 3) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Filter") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 45)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    axis.text.y = element_text(angle = 45),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

```{r filter-perf-all, warning=FALSE, dev = c("png", "pdf")}
perf_all_filters <- df_perf %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  dplyr::filter(filter != "No Filter") %>%
  group_by(learner_group, task.id) %>%
  dplyr::filter(learner_group == "SVM" | learner_group == "RF" | learner_group == "XGBoost")

perf_all_filters %>%
  ggplot(aes(x = rmse_aggr, y = learner_group)) +
  geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 2) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Filter") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 45)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    axis.text.y = element_text(angle = 45),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

Showing the final effect of applying feature selection to a learner for each task.
All filters are summarized into a boxplot whereas using "no filter" appears as a standalone observation.

@@

results_aggr1 %>%
  ggplot(aes(x = perf, y = learner_group)) +
  geom_beeswarm(
    data = results_aggr1[results_aggr1$filter != "NF", ], size = 1.1, shape = 3,
    groupOnX = FALSE, aes(color = "Filter")
  ) +
  geom_point(data = results_aggr1[results_aggr1$filter == "NF", ], 
             size = 2, shape = 19, aes(color = "No Filter")) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", colour = NULL) +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 50)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
  )
```

@@

Showing the final effect of applying feature selection to a learner for each task.
All filters are summarized into a boxplot whereas using "no filter" appears as a standalone observation.

@@

results_aggr2 %>%
  ggplot(aes(x = perf, y = learner_group)) +
  geom_beeswarm(
    data = results_aggr2[results_aggr2$filter != "Borda", ],
    shape = 3, size = 1.1, aes(color = "Simple Filter"),
    groupOnX = FALSE
  ) +
  geom_point(data = results_aggr2[results_aggr2$filter == "Borda", ], 
             shape = 19, size = 2, aes(color = "Borda Filter")) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", colour = NULL) +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 48)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
  )
```

>>>>

```{r}
df_perf <- getBMRPerformances(bm_aggregated, as.df = T) %>%
  mutate(task.id = recode_factor(task.id,
    `defoliation-all-plots-HR` = "HR",
    `defoliation-all-plots-VI` = "VI",
    `defoliation-all-plots-NRI` = "NRI",
    `defoliation-all-plots-HR-NRI` = "HR-NRI",
    `defoliation-all-plots-HR-VI` = "HR-VI",
    `defoliation-all-plots-HR-NRI-VI` = "HR-NRI-VI",
  )) %>%
  tidyr::separate(learner.id, c("learner_group", "filter"),
    remove = FALSE,
    sep = " "
  )
```

@@

```{r performance-results, warning=FALSE, dev = c("png", "pdf")}
results_aggr <- df_perf %>%
  mutate(filter = replace(filter, is.na(filter), "NF")) %>%
  mutate(learner_group = recode_factor(learner_group, `XG` = "XGBOOST")) %>%
  group_by(learner_group, filter, task.id) %>%
  ### get the best performance per learner and task
  # this group_by() & slice() approach is better than summarise() because we can
  # keep additional columns
  # in constrast to summarise which only keeps the grouping columns and the
  # summarised one
  slice(which.min(rmse_aggr)) %>% # this groups the CV iters
  ungroup() %>%
  group_by(task.id, learner_group) %>%
  slice(which.min(rmse_aggr))

results_aggr %>%
  ggplot(aes(x = rmse_aggr, y = task.id)) +
  # geom_jitter(aes(color = learner_group), size = 2, width = 0, height = 0.3) +
  # geom_dotplot(aes(fill = learner_group), binaxis="y",
  #                        stackdir="up") +
  geom_beeswarm(groupOnX = FALSE, aes(color = learner_group), size = 3) +
  scale_color_nejm(breaks = sort(levels(results_aggr$learner_group))) +
  labs(x = "RMSE", y = "Task", color = "Learner") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 70)) +
  geom_label_repel(
    # subset data to remove out of bounds values
    data = results_aggr[results_aggr$rmse_aggr < 100, ],
    # from ggbeeswarm, avoid overlapping of points by labels
    position = position_quasirandom(),
    aes(label = paste0(filter, ",", round(rmse_aggr, 2))),
    size = 2.8,
    min.segment.length = 0.1,
    seed = 123,
    point.padding = 0.5
  ) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    axis.text.y = element_text(angle = 45),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

comb %>%
  ggplot(aes(x = rmse_aggr, y = learner_group)) +
  geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 3) +
  facet_wrap(~task.id) +
  # scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Filter") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 50)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    axis.text.y = element_text(angle = 45),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

comb_borda %>%
  ggplot(aes(x = rmse_aggr, y = learner_group)) +
  geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 3) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Filter") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 50)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    axis.text.y = element_text(angle = 45),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

```{r filter-perf-all, warning=FALSE, dev = c("png", "pdf")}
# perf_all_filters <- df_perf %>%
#   mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
#   dplyr::filter(filter != "No Filter") %>%
#   group_by(learner_group, task.id) %>%
#   dplyr::filter(learner_group == "SVM" | learner_group == "RF" | learner_group == "XGBoost") %>%
#   slice(which.min(rmse_aggr))
#   summarise(perf = mean(rmse_aggr), filter = as.character(filter))
#
# perf_all_filters %>%
#   ggplot(aes(x = rmse_aggr, y = learner_group)) +
#   geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 2) +
#   facet_wrap(~task.id) +
#   scale_color_nejm() +
#   labs(x = "RMSE", y = "Task", color = "Filter") +
#   guides(size = FALSE) +
#   scale_x_continuous(limits = c(30, 45)) +
#   theme_pubr() +
#   theme(
#     panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
#     axis.title.y = element_blank(),
#     axis.text.y = element_text(angle = 45),
#     legend.text = element_text(size = 12),
#     legend.title = element_text(size = 12),
#     plot.margin = unit(c(6, 6, 6, 0), "pt")
#   )
```

@@

Showing the final effect of applying feature selection to a learner for each task.
All filters are colored in the same way whereas using "no filter" appears in a different color.

@@

results_aggr1 %>%
  ggplot(aes(x = perf, y = learner_group)) +
  geom_beeswarm(
    data = results_aggr1[results_aggr1$filter != "NF", ], size = 1.1, shape = 3,
    groupOnX = FALSE, aes(color = "Filter")
  ) +
  geom_point(
    data = results_aggr1[results_aggr1$filter == "NF", ],
    size = 2, shape = 19, aes(color = "No Filter")
  ) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", colour = NULL) +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 50)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
  )
```

@@

Showing the final effect of applying feature selection to a learner for each task.
All filters are summarized into a a single color whereas the "Borda" filter appears in its own color.

@@

results_aggr2 %>%
  ggplot(aes(x = perf, y = learner_group)) +
  geom_beeswarm(
    data = results_aggr2[results_aggr2$filter != "Borda", ],
    shape = 3, size = 1.1, aes(color = "Simple Filter"),
    groupOnX = FALSE
  ) +
  geom_point(
    data = results_aggr2[results_aggr2$filter == "Borda", ],
    shape = 19, size = 2, aes(color = "Borda Filter")
  ) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", colour = NULL) +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(30, 48)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
  )
```
